Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.

### 2022-02-11 ASME_journal/journals-1.3/journals-1.3/TSEA-21-1636_FINAL_SUBMISSION.tex
Update-11/02/2022

%%% use 10pt options with the asme2ej format
\documentclass[10pt]{asme2ej}

\usepackage{epsfig} %% for loading postscript figures
\usepackage{graphicx} %% for loading jpg figures
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

@@

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation. 
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\begin{multicols}{2}
\entry{\textbf{\textit{Variables}}}{}
\entry{$A$}{Area [$m^2$]}
\entry{$A_p$}{Particle surface area [$m^2$]}
\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
\entry{$d_p$}{Particle diameter [$m$]}
\entry{$E$}{Fluid total energy [$J/kg$]}
\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
\entry{$E_p$}{Particle emission power [$W/m^3$]}
\entry{$f_{heat}$}{Near surface char oxidation fraction [-]}
\entry{$f_{p}$}{Forward scattering factor [-]}
\entry{$G$}{Incident radiation [$W/m^2$]}
\entry{$g$}{Gravitational constant [$m/s^2$]}
\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
\entry{$m_{char}$}{Mass of carbon [$kg$]}
\entry{$m_{evap}$}{Mass of moisture [$kg$]}
\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
\entry{$N_{p}$}{Number of particles [-]}
\entry{$P$}{Perimeter [$m$]}
\entry{$p$}{Pressure [$Pa$]}
\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
\entry{$q_{wall}$}{Wall heat flux [$W/m^2$]}
\entry{$R$}{Universal gas constant [$J/molK$]}
\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
\entry{$S$}{Mass source term[$kg/m^3$]}
\entry{$S_m$}{Momentum source term [$N/m^3$]}
\entry{$S_h$}{Energy source term [$W/m^3$]}
\entry{$S_k$}{Species source term [$kg/m^3$]}
\entry{$T_g$}{Gas temperature [$K$]}
\entry{$T_p$}{Particle temperature [$K$]}
\entry{$T_{wall,i}$}{Wall temperature [$K$]}
\entry{$T_{water}$}{Water temperature [$K$]}
\entry{$t$}{Time [$s$]}
\entry{$U_i$}{Over heat transfer coefficient [$W/m^2K$]}
\entry{$u$}{Velocity [$m/s$]}
\entry{$V$}{Volume [$m^3$]}
\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
\entry{$x$}{Quality [-]}
\entry{\textbf{\textit{Greek Variables}}}{}
\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
\entry{$\alpha_H$}{Mixture void fraction [-]}
\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
\entry{$\epsilon_p$}{Particle emissivity [-]}
\entry{$\rho$}{Gas density [$kg/m^3$]}
\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
\entry{$\rho_g$}{Gas density [$kg/m^3$]}
\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
\entry{$\rho_p$}{Particle density [$kg/m^3$]}
\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant [$W/m^2K^4$]}
\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
\entry{$\phi$}{Scalar variable [-]}
\entry{\textbf{\textit{Abbreviations}}}{}
\entry{$MCR$}{Maximum continuous rating}
\entry{$CFPP$}{Coal fired power plant}
\entry{$CFD$}{Computational fluid dynamics}
\entry{$SH$}{Superheater}
\entry{$EE$}{Eulerian-Eulerian}
\entry{$WSGGM$}{Weighted sum of gray gas model}
\entry{$RTE$}{Radiative transport equation}
\entry{$HHV$}{Higher heating value}
\entry{$DAF$}{Dry ash free}
\entry{$AR$}{As-received}
\entry{$PA$}{Primary air}
\entry{$SA$-$AH$}{Secondary air - air heater}
\entry{$SA$}{Secondary air}
\entry{$RH$}{Reheater}
\entry{$ATT$}{Attemperator}
\entry{$EC$}{Economiser}
\end{multicols}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change. However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\

The integration of renewable energy sources will push CFPPs from primarily base load operation to a mid-merit/flexible operating protocol, which includes prolonged operation at low-loads. Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.\\

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).\\

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \cite{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions. The aforementioned research specifically investigated combustion and gas-side effects.\\

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

However, to the authors’ knowledge, the integration of a 1-D process model with a detail CFD model has not been used to investigate the steam side operational performance of a CFPP boiler specifically at low-load. The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\

To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements. Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities. The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture. The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase. This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer. Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.\\

@@

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\

@@

The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate. It then applies the minimum of the three for the source terms calculations. A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}. Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash. The scalar field equations are provided in Tab. \ref{tab_scalars}.\\

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{0.6\textwidth}{p{0.4in} p{0.3\textwidth} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}

>>>>

%%% use 10pt options with the asme2ej format
%\documentclass[10pt]{asme2ej}
\documentclass[11pt,cleanfoot]{asme2ej}

\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

\usepackage{graphicx} %% for loading jpg figures
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{helvet}
\usepackage[hyphens]{url}
%\usepackage{hyphens}
\renewcommand{\familydefault}{\sfdefault}
\pagestyle{fancy}
\lhead{{\it Journal of Thermal Science and Engineering Applications}}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\topmargin 80 pt
\headheight 14 pt
\headsep 30 pt
%\RequirePackage[hyphens]
\usepackage{hyperref}   % to set up hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	citecolor=blue,
	urlcolor=blue,
}
\usepackage[square,numbers]{natbib}

@@

\maketitle    
\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation. 
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\begin{multicols}{2}
\entry{\textbf{\textit{Variables}}}{}
\entry{$A$}{Area [$m^2$]}
\entry{$A_p$}{Particle surface area [$m^2$]}
\entry{$A_{pn}$}{Projected particle surface area [$m^2$]}
\entry{$A_{c}$}{Carbon pre-exponential factor [$s^{-1}$]}
\entry{$A_{vol}$}{Volatile pre-exponential factor [$s^{-1}$]}
\entry{$d_p$}{Particle diameter [$m$]}
\entry{$E$}{Fluid total energy [$J/kg$]}
\entry{$E_{a,c}$}{Carbon activation energy [$J/kmol$]}
\entry{$E_{a,vol}$}{Volatile activation energy [$J/kmol$]}
\entry{$E_p$}{Particle emission power [$W/m^3$]}
\entry{$f_{heat}$}{Surface char oxidation fraction [-]}
\entry{$f_{p}$}{Forward scattering factor [-]}
\entry{$G$}{Incident radiation [$W/m^2$]}
\entry{$g$}{Gravitational constant [$m/s^2$]}
\entry{$h_{fg}$}{Enthalpy of evaporation [$J/kg$]}
\entry{$h_M$}{Mixture enthalpy [$J/kg$]}
\entry{$h_{rxn}$}{Enthalpy of reaction [$J/kg$]}
\entry{$J_k$ }{Species diffusion flux [$m^2/s$]}
\entry{$m_{0,vol}$}{Original mass of volatiles [$kg$]}
\entry{$m_{char}$}{Mass of carbon [$kg$]}
\entry{$m_{evap}$}{Mass of moisture [$kg$]}
\entry{$m_{vol}$}{Mass of volatiles [$kg$]}
\entry{$N_{p}$}{Number of particles [-]}
\entry{$P$}{Perimeter [$m$]}
\entry{$p$}{Pressure [$Pa$]}
\entry{$p_{O_{2}}$}{Partial pressure of $O_2$ [$Pa$]}
\entry{$\dot{Q}_{conv}$}{Convective heat transfer rate [$W$]}
\entry{$\dot{Q}_{rad}$}{Radiative heat transfer rate [$W$]}
\entry{$\dot{Q}_{w}$}{Wall heat transfer rate [$W$]}
\entry{$q_{wall}$}{Wall heat flux [$W/m^2$]}
\entry{$R$}{Universal gas constant [$J/molK$]}
\entry{$R_{c}$}{Carbon reaction rate [$s^{-1}$]}
\entry{$R_{diff}$}{Diffusion reaction rate [$s^{-1}$]}
\entry{$R_{vol}$}{Volatile reaction rate [$s^{-1}$]}
\entry{$S$}{Mass source term[$kg/m^3$]}
\entry{$S_m$}{Momentum source term [$N/m^3$]}
\entry{$S_h$}{Energy source term [$W/m^3$]}
\entry{$S_k$}{Species source term [$kg/m^3$]}
\entry{$T_g$}{Gas temperature [$K$]}
\entry{$T_p$}{Particle temperature [$K$]}
\entry{$T_{wall,i}$}{Wall temperature [$K$]}
\entry{$T_{water}$}{Water temperature [$K$]}
\entry{$t$}{Time [$s$]}
\entry{$U_i$}{Overall heat transfer coefficient}
\entry{}{[$W/m^2K$]}
\entry{$u$}{Velocity [$m/s$]}
\entry{$V$}{Volume [$m^3$]}
\entry{$Y_k$}{Species mass fraction [$kg/kg$]}
\entry{$x$}{Quality [-]}
\entry{\textbf{\textit{Greek Variables}}}{}
\entry{$\alpha_g$}{Gas absorption coefficient [$m^{-1}$]}
\entry{$\alpha_H$}{Mixture void fraction [-]}
\entry{$\alpha_p$}{Particle absorption coefficient [$m^{-1}$]}
\entry{$\epsilon_p$}{Particle emissivity [-]}
\entry{$\rho$}{Gas density [$kg/m^3$]}
\entry{$\rho_{eff}$}{Effective density [$kg/m^3$]}
\entry{$\rho_g$}{Gas density [$kg/m^3$]}
\entry{$\rho_l$}{Liquid density [$kg/m^3$]}
\entry{$\rho_M$}{Mixture density [$kg/m^3$]}
\entry{$\rho_p$}{Particle density [$kg/m^3$]}
\entry{$\sigma_{SB}$}{Stefan-Boltzmann constant}
\entry{}{[$W/m^2K^4$]}
\entry{$\sigma_{p}$}{Particle scattering coefficient [$m^{-1}$]}
\entry{$\phi$}{Scalar variable [-]}
\entry{\textbf{\textit{Abbreviations}}}{}
\entry{$MCR$}{Maximum continuous rating}
\entry{$CFPP$}{Coal fired power plant}
\entry{$CFD$}{Computational fluid dynamics}
\entry{$SH$}{Superheater}
\entry{$EE$}{Eulerian-Eulerian}
\entry{$WSGGM$}{Weighted sum of gray gas model}
\entry{$RTE$}{Radiative transport equation}
\entry{$HHV$}{Higher heating value}
\entry{$DAF$}{Dry ash free}
\entry{$AR$}{As-received}
\entry{$PA$}{Primary air}
\entry{$SA$-$AH$}{Secondary air - air heater}
\entry{$SA$}{Secondary air}
\entry{$RH$}{Reheater}
\entry{$ATT$}{Attemperator}
\entry{$EC$}{Economiser}
\end{multicols}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change. However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.

The integration of renewable energy sources will push CFPPs from primarily base load operation to a mid-merit/flexible operating protocol, which includes prolonged operation at low-loads. Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \cite{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \cite{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions. The aforementioned research specifically investigated combustion and gas-side effects.

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.

However, to the authors’ knowledge, the integration of a 1-D process model with a detail CFD model has not been used to investigate the steam side operational performance of a CFPP boiler specifically at low-load. The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\
To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements. Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.
\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities. The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture. The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase. This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer. Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds averaged forms.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.

@@

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.

@@

The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate. It then applies the minimum of the three for the source terms calculations. A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.
\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}. Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash. The scalar field equations are provided in Tab. \ref{tab_scalars}.
\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{0.8\textwidth}{p{0.1\textwidth} p{0.4\textwidth} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}
